\begin{rSection}{Research Experience}

\begin{rSubsection}{Autonomous Ship Hull Inspection}{2007 - present}{Graduate Student Research Assistant / Post-doctoral Research Fellow}{PeRL Lab}
  \item Implemented real-time visual SLAM front-end and demonstrated on several different real-world ship hulls using Hovering AUV (HAUV).
  \item In collaboration with \ac{MIT} and Bluefin Robotics.
  \item Currently working on real-time vision-based multisession SLAM and high-resolution photomosaic of underwater images.
\end{rSubsection}

\begin{rSubsection}{Multi-AUV Testbed for SLAM and Navigation research}{2007 - 2012}{Graduate Student Research Assistant}{PeRL Lab}
  \item Modified stock Ocean-server's Iver2 into a multi-AUV testbed for robotic navigation research.
  \item Mapped \ac{NOAA} Thunder Bay National Marine Sanctuary using two modified \ac{AUV} equipped with sidescan sonar and optical cameras.
\end{rSubsection}

\begin{rSubsection}{Sensor Data Based Motion Planner project}{2006 - 2007}{Graduate Student Research Assistant}{SNU Robotics Lab}
  \item Participated in the Mobile Manipulation and Movement Coordination subproject.
  \item Researched control algorithm for a mobile manipulator with holonomic/nonholonomic constraint under consideration of mobile robot dynamics.
\end{rSubsection}

\begin{rSubsection}{Modular Robot System Design and Motion Generation Simulator Project}{2005 - 2006}{Graduate Student Research Assistant}{SNU Robotics Lab}
  \item Developed robot hardware interface module for a Lie group dynamics-based simulator.
\end{rSubsection}

\end{rSection}

