\begin{rSection}{Services}

\begin{rSubsection}{Committee}{}{Academic Societies}{}
  \item Workshop Chair, ICRA, 2027.
  \item Workshop Chair, RSS, 2025.
  \item Video and Media Chair, IROS, 2025.
  \item Associate VP, IEEE RAS MAB, 2022--2023.
  \item Activity Funding Committee, IFAC, 2020-present.
  \item Chapter Vice Chair, IEEE OES Korea Chapter, 2019-present.
  \item IROS ICROS Best Application Paper Award Committee, 2019--2022.

  \koronly{\item Program Chair, 한국로봇학술대회 (KROC), 2022.}

  \koronly{\item 평의원, 제어로봇시스템학회 (ICROS), 2019-2022.}

  \item Senior Program Committee, IROS, 2020, 2023.

  \koronly{\item 연구회총무이사, 한국수중수상로봇기술연구회, 한국해양공학회 (KSOE), 2017-2018.}

  \item Publication Chair, IEEE Underwater Technology, 2017.
  \koronly{\item 여성위원장, 제어로봇시스템학회 (ICROS), 2017.}
  \koronly{\item 연구부회장, 수중로봇연구회, 한국로봇학회 (KROS), 2016-2019.}
  \koronly{\item 특허 및 실용신안등록출원심사 자문위원, 2016-2017.}

\end{rSubsection}

%\koronly{
%\begin{rSubsection}{Committee}{}{University / Department}{}
%  \koronly{\item 입시위원회, 2017 -- 2020.}
%  \koronly{\item 교과과정위원회, 2020.}
%  \koronly{\item 학과설명회 (유치위원회), 2018 -- 2020.}
%  \koronly{\item AI대학원 설립 추진위원회, 2018 -- 2020.}

%  \koronly{\item URP 평가위원, 2017-2019.}
%  \koronly{\item URP 운영위원, 2017-2019.}
%  \koronly{\item 대학입학전형 공정관리대책위원회, 2019.}
%  \koronly{\item KI 뉴스레터발간 위원회 (위원장), 2020.}
%
%\end{rSubsection}
%}
% Dissertation Committee
%\input{src/thesis_committee.tex}

% Editorial
\begin{rSubsection}{Editorial Board}{}{}{}
  \item Associate Editor, IJRR, 2023--2025.
  \item Area Chair, RSS, 2023--2024.
  \item Associate Editor, IEEE Transactions on Robotics (T-RO) 2020--2023.
  \item Associate Editor, IEEE Robotics and Automation Letters (RA-L) 2019--2021.
  \item Senior Editor, IEEE UR, 2020, 2021, 2022.
  \item Associate Editor, IEEE IROS, 2020, 2022.
  \item Editor, IFAC CAMS/WROCO, 2019.
\end{rSubsection}

% Workshop and Tutorial
\begin{rSubsection}{Workshop \& Tutorial Organizer}{}{}{}
  \item Workshop on Radar in Robotics: Resilience from Signal to Navigation, ICRA 2024
  \item Workshop on Radar Perception for All-Weather Autonomy, ICRA 2021
  \item Workshop on Reliable Deployment of Machine Learning for Long-Term Autonomy, \sout{ICRA} IROS 2020\\
  (Workshop has postponed to IROS 2020 due to COVID-19).
  \item Workshop on Acoustic based Navigation for Marine Robots, IROS 2017.
\end{rSubsection}

% Reviewer
\begin{rSubsection}{Reviewer}{}{}{}
  \item IEEE Transactions on Robotics (T-RO).
  \item IEEE Transactions on Mechatronics (T-Mech).
  \item IEEE Transactions on Industrial Electronics (T-IE).
  \item IEEE Robotics and Automation Letters (RA-L).
  \item Field Robotics (FR)
  \item Science Report
  \item Journal of Field Robotics (JFR).
  \item AIAA Journal of Guidance, Control, and Dynamics.
  \item Elsevier Robotics and Autonomous Systems (RAS).
  \item Elsevier Ocean Engineering (OE).
  \item ASME Journal of Autonomous Vehicles and Systems.
  \item International Journal of Control, Automation and Systems (IJCAS).
  \item International Journal of Precision Engineering and Manufacturing.
  \item IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS).
  \item IEEE International Conference on Robotics and Automation (ICRA).
  \item Robotics: Science and Systems (RSS).
  \item Conference on Robot Learning (CoRL).
  \item IEEE Intelligent Transportation Systems Conference (ITSC).
  \item International Conference on Control, Automation and Systems (ICCAS).
\end{rSubsection}


\end{rSection}
